---
title: "FacebookDataAnalysis"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Import Data
```{r}
fd = read.csv('pseudo_facebook.tsv',sep ='\t')
```

##Histogram of Birthday
31st of of every month has low count which makes sense as not every month has 31 days
1st day of month had a huge peak which seemed weird.
```{r warning=FALSE}
# install.packages('ggplot2')
library(ggplot2)
qplot(x= dob_day, data = fd, binwidth = .5, color = 'black', fill = '#F79420') + 
  scale_x_continuous(breaks = 1:31)
```
  
  Later I tried to dive in further to get more insights.
I saw that most of the peak is for 1st January which could be a default setting for the users who did not add their birthdays.
```{r warning=FALSE}
qplot(x= dob_day, data = fd, binwidth = .5, color = 'black', fill = '#F79420') + 
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~dob_month)
```

##Histogram of Friendcount
Its a right skewed data with most entries in the range of 0 to 1000 
```{r warning=FALSE}
qplot(x= friend_count, data = fd, binwidth = 3, color = 'black', fill = '#F79420')
```


Setting a limit on axis
```{r warning=FALSE}
qplot(x= friend_count, data = fd, binwidth = 10, color = 'black', fill = '#F79420') + 
  scale_x_continuous(limits = c(0,1000))
```

Analyzing friend count by gender
```{r echo = FALSE,message=FALSE, warning=FALSE}
qplot(x= friend_count, data = na.omit(fd), binwidth = 10, color = 'black', fill = '#F79420') + 
  scale_x_continuous(limits = c(0,1000)) +
  facet_wrap(~gender) 
```
#statistics by gender solution
```{r warning=FALSE}
by(fd$friend_count, fd$gender, summary)
```
#log transformation works better on skewed data
```{r warning=FALSE}
p = qplot(x= friend_count, data = fd, fill = '#F79420')
p1 = qplot(x= log10(friend_count + 1), data = fd, fill = '#F79420')
#install.packages('gridExtra')
library(gridExtra)
grid.arrange(p,p1, ncol = 1)

```
#Frequency Polygon to comapare counts histograms by gender
```{r warning=FALSE}
ggplot(aes(x = friend_count, y = ..count../sum(..count..)), data = subset(fd, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count') + 
  ylab('Percentage of users with that friend count')
```

#Analyzing likes by gender
```{r warning=FALSE, echo=FALSE, message=FALSE}
ggplot(aes(x = www_likes), data = subset(fd, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender)) + 
  scale_x_log10()+
  xlab('Likes') + 
  ylab('Users with that friend count')
```

# Analysis to see who initiates a friend request on an average
```{r warning=FALSE, echo=FALSE, message=FALSE}
qplot(x = gender, y = friendships_initiated, data = subset(fd, !is.na(gender)),geom = 'boxplot', color = gender)+
  coord_cartesian(ylim = c(0,500))
  
```

#checking if facebook should concerntrate on their mobile app
For this we can check what percent of people actually use facebook on their mobile
This can be found out using mobile_like attribute in the dataset.
```{r warning=FALSE, echo=FALSE, message=FALSE}
fd$mobile_chekin = ifelse(fd$mobile_likes>0,1,0)
table(fd$mobile_chekin)
```
This tells that more than 50 percent people use facebook on mobile

