---
title: "Facebook Data Analysis"
author: Chinmay Abhyankar
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
I am analyzing psuedo facebook data which means this data has been modified for security reasons.This data has 99003 records and 15 attributes.
The attrributes are as follows:
 "userid","age","dob_day", "dob_year", "dob_month", "gender", tenure", "friend_count", "friendships_initiated", "likes", "likes_received", "mobile_likes", "mobile_likes_received", "www_likes", "www_likes_received"   
 
##Import Data
```{r}
fd = read.csv('pseudo_facebook.tsv',sep ='\t')
```

##Histogram of Birthday
31st of of every month has low count which makes sense as not every month has 31 days
1st day of month had a huge peak which seemed weird.
```{r warning=FALSE}
# install.packages('ggplot2')
library(ggplot2)
qplot(x= dob_day, data = fd, binwidth = .5, fill = 'red') + 
  scale_x_continuous(breaks = 1:31)
```
  
  Later I tried to dive in further to get more insights.
I saw that most of the peak is for 1st January which could be a default setting for the users who did not add their birthdays.
```{r warning=FALSE}
qplot(x= dob_day, data = fd, binwidth = .5,fill = 'red') + 
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~dob_month)
```

##Histogram of Friendcount
Its a right skewed data with most entries in the range of 0 to 1000 
```{r warning=FALSE}
qplot(x= friend_count, data = fd, binwidth = 3,fill = 'red')
```


Setting a limit on axis
```{r warning=FALSE}
qplot(x= friend_count, data = fd, binwidth = 10,fill = 'red') + 
  scale_x_continuous(limits = c(0,1000))
```

Analyzing friend count by gender
```{r echo = FALSE,message=FALSE, warning=FALSE}
qplot(x= friend_count, data = na.omit(fd), binwidth = 10,fill = 'red') + 
  scale_x_continuous(limits = c(0,1000)) +
  facet_wrap(~gender) 
```

#statistics by gender solution
```{r warning=FALSE}
by(fd$friend_count, fd$gender, summary)
```
#log transformation works better on skewed data
```{r warning=FALSE}
p = qplot(x= friend_count, data = fd, fill = 'red')
p1 = qplot(x= log10(friend_count + 1), data = fd, fill = 'red')
#install.packages('gridExtra')
library(gridExtra)
grid.arrange(p,p1, ncol = 1)

```

#Frequency Polygon to comapare counts histograms by gender
```{r warning=FALSE}
ggplot(aes(x = friend_count, y = ..count../sum(..count..)), data = subset(fd, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count') + 
  ylab('Percentage of users with that friend count')
```

#Analyzing likes by gender
```{r warning=FALSE, echo=FALSE, message=FALSE}
ggplot(aes(x = www_likes), data = subset(fd, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender)) + 
  scale_x_log10()+
  xlab('Likes') + 
  ylab('Users with that friend count')
```

# Analysis to see who initiates a friend request on an average
```{r warning=FALSE, echo=FALSE, message=FALSE}
qplot(x = gender, y = friendships_initiated, data = subset(fd, !is.na(gender)),geom = 'boxplot', color = gender)+
  coord_cartesian(ylim = c(0,500))
  
```

#checking if facebook should concerntrate on their mobile app
For this we can check what percent of people actually use facebook on their mobile
This can be found out using mobile_like attribute in the dataset.
```{r warning=FALSE, echo=FALSE, message=FALSE}
fd$mobile_chekin = ifelse(fd$mobile_likes>0,1,0)
table(fd$mobile_chekin)
```
This tells that more than 50 percent people use facebook on mobile

#Analyzing Friend counts conditional on age
```{r warning=FALSE, echo=FALSE, message=FALSE}
#summary(fd$age)
ggplot(aes(x = age, y = friend_count), data = fd) +geom_point(color = 'orange') +
  xlim(13,93) 
```

As there are too many points let us understand the density of the points in the graph.
Let us reduce the effect of overplotting
```{r warning=FALSE, echo=FALSE, message=FALSE}
ggplot(aes(x = age, y = friend_count), data = fd) +geom_jitter(alpha = 1/20,color = 'orange')+
  xlim(13,93)
```

It seems that data points are mostly concerntrated in friend_count range of (0,1000) and age range of (0,75)

Now let us have a look at the quantile distribution of the data
Let us reduce the effect of overplotting
```{r warning=FALSE, echo=FALSE, message=FALSE}
ggplot(aes(x = age, y = friend_count), data = fd) + xlim(13,93) + 
geom_point(alpha = 1/20,color = 'orange', position = position_jitter(h = 0)) +
   coord_trans(y = 'sqrt') +
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat= 'summary', fun.y = quantile, fun.args = list(probs = .9), linetype = 2) +
  geom_line(stat= 'summary', fun.y = quantile, fun.args = list(probs = .1), linetype = 2)
```
